Using Metric Space Indexing for Complete and Efficient Record Linkage

### 2018-04-20 paper.tex
CRC

\institute{School of Computer Science, University of St Andrews,
St Andrews, Scotland. Contact: \email{\{ozgur.akgun, alan.dearle, graham.kirby\}@st-andrews.ac.uk}
\and
Research School of Computer Science, The Australian National University,\\
Canberra, Australia. Contact: \email{peter.christen@anu.edu.au}}

@@

\begin{figure}
\centering
\begin{subfigure}{.47\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotLQ-cora-brute}
\vspace{-6mm}
\caption{Brute Force}
\end{subfigure}%
~~
\begin{subfigure}{.47\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotLQ-cora-mtree}
\vspace{-6mm}
\caption{M-tree}
\end{subfigure} \vspace{3mm}

\begin{subfigure}{.47\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotLQ-cora-trad-authors}
\vspace{-6mm}
\caption{Blocking on `authors' attribute}
\end{subfigure}%
~~
\begin{subfigure}{.47\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotLQ-cora-trad-title}
\vspace{-6mm}
\caption{Blocking on `title' attribute}
\end{subfigure} \vspace{3mm}

\begin{subfigure}{.47\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotLQ-cora-trad-year}
\vspace{-6mm}
\caption{Blocking on `publication year' attr.}
\end{subfigure}%
~~
\begin{subfigure}{.47\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotLQ-cora-trad-combined}
\vspace{-6mm}
\caption{Blocking using the union of all attrs.}
\end{subfigure} \vspace{3mm}

\begin{subfigure}{.47\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotLQ-cora-lsh-2-2}
\vspace{-6mm}
\caption{LSH using 2 bands of size 2}
\end{subfigure}%
~~
\begin{subfigure}{.47\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotLQ-cora-lsh-2-10}
\vspace{-6mm}
\caption{LSH using 2 bands of size 10}
\end{subfigure} \vspace{3mm}

\begin{subfigure}{.47\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotLQ-cora-lsh-10-2}
\vspace{-6mm}
\caption{LSH using 10 bands of size 2}
\end{subfigure}%
~~
\begin{subfigure}{.47\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotLQ-cora-lsh-10-10}
\vspace{-6mm}
\caption{LSH using 10 bands of size 10}
\end{subfigure}
\caption{Linkage results on the Cora dataset.}
\label{cora-quality}
\end{figure}

@@

\begin{figure}[t]
\centering
\begin{subfigure}{.47\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotLQ-skye-mtree}
\vspace{-6mm}
\caption{M-tree on Isle of Skye dataset\label{skye-quality-mtree}}
\end{subfigure}%
~~
\begin{subfigure}{.47\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotLQ-kilmarnock-mtree}
\vspace{-6mm}
\caption{M-tree on Kilmarnock dataset \label{kilmarnock-quality-mtree}}
\end{subfigure} \vspace{5mm}

\begin{subfigure}{.47\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotFs-skye-f}
\vspace{-6mm}
\caption{F-measure on Isle of Skye dataset \\ with M-tree and all
LSH configurations}
\end{subfigure}%
~~
\begin{subfigure}{.47\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotFs-kilmarnock-f}
\vspace{-6mm}
\caption{F-measure on Kilmarnock dataset \\ with M-tree and all LSH configurations}
\end{subfigure}
\caption{Linkage results on the demographic datasets.}
\label{demography-quality}
\end{figure}

@@

\bibliographystyle{splncs03}
\bibliography{paper.bib}

>>>>

\institute{School of Computer Science, University of St Andrews, St Andrews, Scotland.
\\ \email{\{ozgur.akgun, alan.dearle, graham.kirby\}@st-andrews.ac.uk}
\and
Research School of Computer Science, The Australian National University, Canberra, Australia.
\\ \email{peter.christen@anu.edu.au}}

@@

\begin{figure}
\centering
\begin{subfigure}{.47\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotLQ-cora-brute}
% \vspace{-6mm}
\caption{Brute Force}
\end{subfigure}%
~~
\begin{subfigure}{.47\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotLQ-cora-mtree}
% \vspace{-6mm}
\caption{M-tree}
\end{subfigure} % \vspace{3mm}

\begin{subfigure}{.47\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotLQ-cora-trad-authors}
% \vspace{-6mm}
\caption{Blocking on `authors' attribute}
\end{subfigure}%
~~
\begin{subfigure}{.47\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotLQ-cora-trad-title}
% \vspace{-6mm}
\caption{Blocking on `title' attribute}
\end{subfigure} % \vspace{3mm}

\begin{subfigure}{.47\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotLQ-cora-trad-year}
% \vspace{-6mm}
\caption{Blocking on `publication year' attr.}
\end{subfigure}%
~~
\begin{subfigure}{.47\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotLQ-cora-trad-combined}
% \vspace{-6mm}
\caption{Blocking using the union of all attrs.}
\end{subfigure} % \vspace{3mm}

\begin{subfigure}{.47\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotLQ-cora-lsh-2-2}
% \vspace{-6mm}
\caption{LSH using 2 bands of size 2}
\end{subfigure}%
~~
\begin{subfigure}{.47\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotLQ-cora-lsh-2-10}
% \vspace{-6mm}
\caption{LSH using 2 bands of size 10}
\end{subfigure} % \vspace{3mm}

\begin{subfigure}{.47\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotLQ-cora-lsh-10-2}
% \vspace{-6mm}
\caption{LSH using 10 bands of size 2}
\end{subfigure}%
~~
\begin{subfigure}{.47\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotLQ-cora-lsh-10-10}
% \vspace{-6mm}
\caption{LSH using 10 bands of size 10}
\end{subfigure}
\caption{Linkage results on the Cora dataset.}
\label{cora-quality}
\end{figure}

@@

\begin{figure}[t]
\centering
\begin{subfigure}{.47\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotLQ-skye-mtree}
% \vspace{-6mm}
\caption{M-tree on Isle of Skye dataset\label{skye-quality-mtree}}
\end{subfigure}%
~~
\begin{subfigure}{.47\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotLQ-kilmarnock-mtree}
% \vspace{-6mm}
\caption{M-tree on Kilmarnock dataset \label{kilmarnock-quality-mtree}}
\end{subfigure} % \vspace{5mm}

\begin{subfigure}{.47\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotFs-skye-f}
% \vspace{-6mm}
\caption{F-measure on Isle of Skye dataset \\ with M-tree and all
LSH configurations}
\end{subfigure}%
~~
\begin{subfigure}{.47\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotFs-kilmarnock-f}
% \vspace{-6mm}
\caption{F-measure on Kilmarnock dataset \\ with M-tree and all LSH configurations}
\end{subfigure}
\caption{Linkage results on the demographic datasets.}
\label{demography-quality}
\end{figure}

@@

\bibliographystyle{splncs04}
\bibliography{paper.bib}
